---
title: "Analysis with replacement"
output: html_document
---

# This file contains code for Replacement analysis

### large scale testing (null distribution)
```{r}
max2000_rank_dim <- read_csv("~/max2000_rank_dim.txt", col_names = FALSE)

max2000_rank_dim$X1<- gsub("[^0-9]", "",max2000_rank_dim$X1)
max2000_rank_dim$X3<- gsub("[^0-9]", "",max2000_rank_dim$X3)

max2000_rank_dim<- matrix(as.numeric(max2000_rank_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(max2000_rank_dim,max2000_rank_dim,max2000_rank_dim,max2000_rank_dim), dim=c(20,20,4))

allt<- array(0,dim=c(20,20,500))
for (m in 1:500){

group1<- sample(1:4,2)  
all<- seq(1,4,1)
group2<- all[is.na(pmatch(all,group1))]

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,group1])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,group2])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,group1[1]]-x1[1,j])^2,(large_scale[i,j,group1[2]]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,group2[1]]-x2[1,j])^2,(large_scale[i,j,group2[2]]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/2*1/4
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
allt[,,m] <- t
print(m)
}

allt[is.na(allt)]<- 0
cvt<- matrix(0,ncol=20,nrow=20)

for (i in 1:20){
  for (j in 1:20){
    cvt[i,j]<- mean(allt[i,j,1:20])
  }
}

#hist(allt)
z<- qnorm(pt(cvt,13))
z_null<- z
z_null[is.na(z_null)] <- 0
hist(z_null,30)

qqnorm(z_null)
qqline(z_null)
```


### large scale testing (4 samples)
```{r}
max2000_rank_rp1_dim<- read_csv("~/max2000_rank_rp1_H0_dim.txt", col_names = FALSE)
max2000_rank_rp2_dim<- read_csv("~/max2000_rank_rp2_H0_dim.txt", col_names = FALSE)
max2000_rank_rp3_dim<- read_csv("~/max2000_rank_rp3_H0_dim.txt", col_names = FALSE)
max2000_rank_rp4_dim<- read_csv("~/max2000_rank_rp4_H0_dim.txt", col_names = FALSE)

max2000_rank_rp1_dim$X1<- gsub("[^0-9]", "",max2000_rank_rp1_dim$X1)
max2000_rank_rp1_dim$X3<- gsub("[^0-9]", "",max2000_rank_rp1_dim$X3)
max2000_rank_rp2_dim$X1<- gsub("[^0-9]", "",max2000_rank_rp2_dim$X1)
max2000_rank_rp2_dim$X3<- gsub("[^0-9]", "",max2000_rank_rp2_dim$X3)
max2000_rank_rp3_dim$X1<- gsub("[^0-9]", "",max2000_rank_rp3_dim$X1)
max2000_rank_rp3_dim$X3<- gsub("[^0-9]", "",max2000_rank_rp3_dim$X3)
max2000_rank_rp4_dim$X1<- gsub("[^0-9]", "",max2000_rank_rp4_dim$X1)
max2000_rank_rp4_dim$X3<- gsub("[^0-9]", "",max2000_rank_rp4_dim$X3)

max2000_rank_rp1_dim<- matrix(as.numeric(max2000_rank_rp1_dim$X3), ncol=20, byrow=F)
max2000_rank_rp2_dim<- matrix(as.numeric(max2000_rank_rp2_dim$X3), ncol=20, byrow=F)
max2000_rank_rp3_dim<- matrix(as.numeric(max2000_rank_rp3_dim$X3), ncol=20, byrow=F)
max2000_rank_rp4_dim<- matrix(as.numeric(max2000_rank_rp4_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(max2000_rank_rp1_dim,max2000_rank_rp2_dim,max2000_rank_rp3_dim,max2000_rank_rp4_dim, max2000_rank_dim,max2000_rank_dim,max2000_rank_dim,max2000_rank_dim), dim=c(20,20,8))

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,1:4])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,5:8])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,1]-x1[1,j])^2,(large_scale[i,j,2]-x1[1,j])^2,(large_scale[i,j,3]-x1[1,j])^2,(large_scale[i,j,4]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,5]-x2[1,j])^2,(large_scale[i,j,6]-x2[1,j])^2,(large_scale[i,j,7]-x2[1,j])^2,(large_scale[i,j,8]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/6*1/8
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
hist(t)
z<- qnorm(pt(t,6))
z[is.na(z)]<- 0
hist(z)

null_dist<- density(z_null)
hist(z,30)
lines(null_dist)

h<-hist(z_null, breaks=10) 
xfit<-seq(min(z_null),max(z_null),length=40) 
yfit<-dnorm(xfit,mean=mean(z_null),sd=sd(z_null)) 
yfit <- yfit*diff(h$mids[1:2])*length(z_null)  
lines(xfit, yfit, col="blue", lwd=2)

hist(z,30,ylim=c(0,350),xlab="z-scores", main="Histogram of z-scores")
lines(xfit, yfit, col="blue", lwd=2)

sum(z>quantile(z_null,1-0.05/400),na.rm = T)
table<- z
hist(z)
ifelse(z>quantile(z_null,1-0.05/400),1,0)

```

### large scale testing with replacement data sets (null as random_from_wiki)
```{r}
wiki_sample1_dim<- read_csv("~/wiki_sample1_dim.txt", col_names = FALSE)
wiki_sample2_dim<- read_csv("~/wiki_sample2_dim.txt", col_names = FALSE)
wiki_sample3_dim<- read_csv("~/wiki_sample3_dim.txt", col_names = FALSE)
wiki_sample4_dim<- read_csv("~/wiki_sample4_dim.txt", col_names = FALSE)
wiki_sample5_dim<- read_csv("~/wiki_sample5_dim.txt", col_names = FALSE)
wiki_sample6_dim<- read_csv("~/wiki_sample6_dim.txt", col_names = FALSE)
wiki_sample7_dim<- read_csv("~/wiki_sample7_dim.txt", col_names = FALSE)
wiki_sample8_dim<- read_csv("~/wiki_sample8_dim.txt", col_names = FALSE)
wiki_sample9_dim<- read_csv("~/wiki_sample9_dim.txt", col_names = FALSE)
wiki_sample10_dim<- read_csv("~/wiki_sample10_dim.txt", col_names = FALSE)
wiki_sample11_dim<- read_csv("~/wiki_sample11_dim.txt", col_names = FALSE)
wiki_sample12_dim<- read_csv("~/wiki_sample12_dim.txt", col_names = FALSE)
wiki_sample13_dim<- read_csv("~/wiki_sample13_dim.txt", col_names = FALSE)
wiki_sample14_dim<- read_csv("~/wiki_sample14_dim.txt", col_names = FALSE)
wiki_sample15_dim<- read_csv("~/wiki_sample15_dim.txt", col_names = FALSE)

wiki_sample1_dim$X1<- gsub("[^0-9]", "",wiki_sample1_dim$X1)
wiki_sample1_dim$X3<- gsub("[^0-9]", "",wiki_sample1_dim$X3)
wiki_sample2_dim$X1<- gsub("[^0-9]", "",wiki_sample2_dim$X1)
wiki_sample2_dim$X3<- gsub("[^0-9]", "",wiki_sample2_dim$X3)
wiki_sample3_dim$X1<- gsub("[^0-9]", "",wiki_sample3_dim$X1)
wiki_sample3_dim$X3<- gsub("[^0-9]", "",wiki_sample3_dim$X3)
wiki_sample4_dim$X1<- gsub("[^0-9]", "",wiki_sample4_dim$X1)
wiki_sample4_dim$X3<- gsub("[^0-9]", "",wiki_sample4_dim$X3)
wiki_sample5_dim$X1<- gsub("[^0-9]", "",wiki_sample5_dim$X1)
wiki_sample5_dim$X3<- gsub("[^0-9]", "",wiki_sample5_dim$X3)
wiki_sample6_dim$X1<- gsub("[^0-9]", "",wiki_sample6_dim$X1)
wiki_sample6_dim$X3<- gsub("[^0-9]", "",wiki_sample6_dim$X3)
wiki_sample7_dim$X1<- gsub("[^0-9]", "",wiki_sample7_dim$X1)
wiki_sample7_dim$X3<- gsub("[^0-9]", "",wiki_sample7_dim$X3)
wiki_sample8_dim$X1<- gsub("[^0-9]", "",wiki_sample8_dim$X1)
wiki_sample8_dim$X3<- gsub("[^0-9]", "",wiki_sample8_dim$X3)
wiki_sample9_dim$X1<- gsub("[^0-9]", "",wiki_sample9_dim$X1)
wiki_sample9_dim$X3<- gsub("[^0-9]", "",wiki_sample9_dim$X3)
wiki_sample10_dim$X1<- gsub("[^0-9]", "",wiki_sample10_dim$X1)
wiki_sample10_dim$X3<- gsub("[^0-9]", "",wiki_sample10_dim$X3)
wiki_sample11_dim$X1<- gsub("[^0-9]", "",wiki_sample11_dim$X1)
wiki_sample11_dim$X3<- gsub("[^0-9]", "",wiki_sample11_dim$X3)
wiki_sample12_dim$X1<- gsub("[^0-9]", "",wiki_sample12_dim$X1)
wiki_sample12_dim$X3<- gsub("[^0-9]", "",wiki_sample12_dim$X3)
wiki_sample13_dim$X1<- gsub("[^0-9]", "",wiki_sample13_dim$X1)
wiki_sample13_dim$X3<- gsub("[^0-9]", "",wiki_sample13_dim$X3)
wiki_sample14_dim$X1<- gsub("[^0-9]", "",wiki_sample14_dim$X1)
wiki_sample14_dim$X3<- gsub("[^0-9]", "",wiki_sample14_dim$X3)
wiki_sample15_dim$X1<- gsub("[^0-9]", "",wiki_sample15_dim$X1)
wiki_sample15_dim$X3<- gsub("[^0-9]", "",wiki_sample15_dim$X3)

wiki_sample1_dim<- matrix(as.numeric(wiki_sample1_dim$X3), ncol=20, byrow=F)
wiki_sample2_dim<- matrix(as.numeric(wiki_sample2_dim$X3), ncol=20, byrow=F)
wiki_sample3_dim<- matrix(as.numeric(wiki_sample3_dim$X3), ncol=20, byrow=F)
wiki_sample4_dim<- matrix(as.numeric(wiki_sample4_dim$X3), ncol=20, byrow=F)
wiki_sample5_dim<- matrix(as.numeric(wiki_sample5_dim$X3), ncol=20, byrow=F)
wiki_sample6_dim<- matrix(as.numeric(wiki_sample6_dim$X3), ncol=20, byrow=F)
wiki_sample7_dim<- matrix(as.numeric(wiki_sample7_dim$X3), ncol=20, byrow=F)
wiki_sample8_dim<- matrix(as.numeric(wiki_sample8_dim$X3), ncol=20, byrow=F)
wiki_sample9_dim<- matrix(as.numeric(wiki_sample9_dim$X3), ncol=20, byrow=F)
wiki_sample10_dim<- matrix(as.numeric(wiki_sample10_dim$X3), ncol=20, byrow=F)
wiki_sample11_dim<- matrix(as.numeric(wiki_sample11_dim$X3), ncol=20, byrow=F)
wiki_sample12_dim<- matrix(as.numeric(wiki_sample12_dim$X3), ncol=20, byrow=F)
wiki_sample13_dim<- matrix(as.numeric(wiki_sample13_dim$X3), ncol=20, byrow=F)
wiki_sample14_dim<- matrix(as.numeric(wiki_sample14_dim$X3), ncol=20, byrow=F)
wiki_sample15_dim<- matrix(as.numeric(wiki_sample15_dim$X3), ncol=20, byrow=F)


large_scale<- array(c(wiki_sample1_dim, wiki_sample2_dim, wiki_sample3_dim, wiki_sample4_dim, wiki_sample5_dim, wiki_sample6_dim, wiki_sample7_dim, wiki_sample8_dim, wiki_sample9_dim, wiki_sample10_dim, wiki_sample11_dim, wiki_sample12_dim, wiki_sample13_dim, wiki_sample14_dim, wiki_sample15_dim), dim=c(20,20,15))


allt<- array(0,dim=c(20,20,500))
for (m in 1:500){

group1<- sample(1:15,7)  
all<- seq(1,15,1)
group2<- all[is.na(pmatch(all,group1))]

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,group1])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,group2])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,group1[1]]-x1[1,j])^2,(large_scale[i,j,group1[2]]-x1[1,j])^2,(large_scale[i,j,group1[3]]-x1[1,j])^2,(large_scale[i,j,group1[4]]-x1[1,j])^2,(large_scale[i,j,group1[5]]-x1[1,j])^2,(large_scale[i,j,group1[6]]-x1[1,j])^2,(large_scale[i,j,group1[7]]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,group2[1]]-x2[1,j])^2,(large_scale[i,j,group2[2]]-x2[1,j])^2,(large_scale[i,j,group2[3]]-x2[1,j])^2,
                 (large_scale[i,j,group2[4]]-x2[1,j])^2,(large_scale[i,j,group2[5]]-x2[1,j])^2,(large_scale[i,j,group2[6]]-x2[1,j])^2,(large_scale[i,j,group2[7]]-x2[1,j])^2,(large_scale[i,j,group2[8]]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/13*1/15
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
allt[,,m] <- t
print(m)
}

allt[is.na(allt)]<- 0
cvt<- matrix(0,ncol=20,nrow=20)

for (i in 1:20){
  for (j in 1:20){
    cvt[i,j]<- mean(allt[i,j,1:20])
  }
}

#hist(allt)
z<- qnorm(pt(cvt,13))
z_null<- z
z_null[is.na(z_null)] <- 0
hist(z_null,30)

qqnorm(z_null)
qqline(z_null)

```

### replacement datasets for random_from_wiki
```{r}
options(scipen=999)
random_from_wiki_2000 <- read_delim("~/random_from_wiki_2000.txt"," ", escape_double = FALSE, trim_ws = TRUE)
random1_2000 <- read_delim("~/random1_2000.txt", " ", escape_double = FALSE, trim_ws = TRUE)
random_from_wiki_2000<- random_from_wiki_2000[4:2003,]
random1_2000<- random1_2000[4:2003,]
random_from_wiki_2000<- matrix(as.numeric(unlist(random_from_wiki_2000)),nrow=2000)
random1_2000<- matrix(as.numeric(unlist(random1_2000)),nrow=2000)

### rp 2
rp<- sample(1:2000,2)
random_from_wiki_2000_rp2<- random_from_wiki_2000
random_from_wiki_2000_rp2[rp,1:200]<- random1_2000[rp,1:200]

### rp 4
rp<- sample(1:2000,4)
random_from_wiki_2000_rp4<- random_from_wiki_2000
random_from_wiki_2000_rp4[rp,1:200]<- random1_2000[rp,1:200]

### rp 6
rp<- sample(1:2000,6)
random_from_wiki_2000_rp6<- random_from_wiki_2000
random_from_wiki_2000_rp6[rp,1:200]<- random1_2000[rp,1:200]


### rp 8
rp<- sample(1:2000,8)
random_from_wiki_2000_rp8<- random_from_wiki_2000
random_from_wiki_2000_rp8[rp,1:200]<- random1_2000[rp,1:200]


### rp 10
rp<- sample(1:2000,10)
random_from_wiki_2000_rp10<- random_from_wiki_2000
random_from_wiki_2000_rp10[rp,1:200]<- random1_2000[rp,1:200]


### rp 12
rp<- sample(1:2000,12)
random_from_wiki_2000_rp12<- random_from_wiki_2000
random_from_wiki_2000_rp12[rp,1:200]<- random1_2000[rp,1:200]


### rp 14
rp<- sample(1:2000,14)
random_from_wiki_2000_rp14<- random_from_wiki_2000
random_from_wiki_2000_rp14[rp,1:200]<- random1_2000[rp,1:200]


### rp 16
rp<- sample(1:2000,16)
random_from_wiki_2000_rp16<- random_from_wiki_2000
random_from_wiki_2000_rp16[rp,1:200]<- random1_2000[rp,1:200]


### rp 18
rp<- sample(1:2000,18)
random_from_wiki_2000_rp18<- random_from_wiki_2000
random_from_wiki_2000_rp18[rp,1:200]<- random1_2000[rp,1:200]


### rp 20
rp<- sample(1:2000,20)
random_from_wiki_2000_rp20<- random_from_wiki_2000
random_from_wiki_2000_rp20[rp,1:200]<- random1_2000[rp,1:200]


### rp 22
rp<- sample(1:2000,22)
random_from_wiki_2000_rp22<- random_from_wiki_2000
random_from_wiki_2000_rp22[rp,1:200]<- random1_2000[rp,1:200]


### rp 24
rp<- sample(1:2000,24)
random_from_wiki_2000_rp24<- random_from_wiki_2000
random_from_wiki_2000_rp24[rp,1:200]<- random1_2000[rp,1:200]


### rp 26
rp<- sample(1:2000,26)
random_from_wiki_2000_rp26<- random_from_wiki_2000
random_from_wiki_2000_rp26[rp,1:200]<- random1_2000[rp,1:200]


### rp 28
rp<- sample(1:2000,28)
random_from_wiki_2000_rp28<- random_from_wiki_2000
random_from_wiki_2000_rp28[rp,1:200]<- random1_2000[rp,1:200]


### rp 30
rp<- sample(1:2000,30)
random_from_wiki_2000_rp30<- random_from_wiki_2000
random_from_wiki_2000_rp30[rp,1:200]<- random1_2000[rp,1:200]

# write.table(random_from_wiki_2000_rp2, "random_from_wiki_2000_rp2.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp4, "random_from_wiki_2000_rp4.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp6, "random_from_wiki_2000_rp6.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp8, "random_from_wiki_2000_rp8.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp10, "random_from_wiki_2000_rp10.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp12, "random_from_wiki_2000_rp12.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp14, "random_from_wiki_2000_rp14.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp16, "random_from_wiki_2000_rp16.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp18, "random_from_wiki_2000_rp18.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp20, "random_from_wiki_2000_rp20.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp22, "random_from_wiki_2000_rp22.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp24, "random_from_wiki_2000_rp24.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp26, "random_from_wiki_2000_rp26.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp28, "random_from_wiki_2000_rp28.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp30, "random_from_wiki_2000_rp30.txt",row.names=FALSE, na="", col.names = FALSE)
```

### large scale testing on replacement datasets (random_from_wiki)
```{r}
random_from_wiki_2000_rp2_dim<- read_csv("~/random_from_wiki_2000_rp2_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp4_dim<- read_csv("~/random_from_wiki_2000_rp4_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp6_dim<- read_csv("~/random_from_wiki_2000_rp6_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp8_dim<- read_csv("~/random_from_wiki_2000_rp8_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp10_dim<- read_csv("~/random_from_wiki_2000_rp10_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp12_dim<- read_csv("~/random_from_wiki_2000_rp12_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp14_dim<- read_csv("~/random_from_wiki_2000_rp14_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp16_dim<- read_csv("~/random_from_wiki_2000_rp16_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp18_dim<- read_csv("~/random_from_wiki_2000_rp18_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp20_dim<- read_csv("~/random_from_wiki_2000_rp20_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp22_dim<- read_csv("~/random_from_wiki_2000_rp22_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp24_dim<- read_csv("~/random_from_wiki_2000_rp24_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp26_dim<- read_csv("~/random_from_wiki_2000_rp26_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp28_dim<- read_csv("~/random_from_wiki_2000_rp28_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp30_dim<- read_csv("~/random_from_wiki_2000_rp30_H0_dim.txt", col_names = FALSE)

random_from_wiki_2000_rp2_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp2_dim$X1)
random_from_wiki_2000_rp2_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp2_dim$X3)
random_from_wiki_2000_rp4_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp4_dim$X1)
random_from_wiki_2000_rp4_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp4_dim$X3)
random_from_wiki_2000_rp6_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp6_dim$X1)
random_from_wiki_2000_rp6_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp6_dim$X3)
random_from_wiki_2000_rp8_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp8_dim$X1)
random_from_wiki_2000_rp8_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp8_dim$X3)
random_from_wiki_2000_rp10_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp10_dim$X1)
random_from_wiki_2000_rp10_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp10_dim$X3)
random_from_wiki_2000_rp12_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp12_dim$X1)
random_from_wiki_2000_rp12_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp12_dim$X3)
random_from_wiki_2000_rp14_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp14_dim$X1)
random_from_wiki_2000_rp14_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp14_dim$X3)
random_from_wiki_2000_rp16_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp16_dim$X1)
random_from_wiki_2000_rp16_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp16_dim$X3)
random_from_wiki_2000_rp18_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp18_dim$X1)
random_from_wiki_2000_rp18_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp18_dim$X3)
random_from_wiki_2000_rp20_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp20_dim$X1)
random_from_wiki_2000_rp20_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp20_dim$X3)
random_from_wiki_2000_rp22_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp22_dim$X1)
random_from_wiki_2000_rp22_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp22_dim$X3)
random_from_wiki_2000_rp24_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp24_dim$X1)
random_from_wiki_2000_rp24_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp24_dim$X3)
random_from_wiki_2000_rp26_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp26_dim$X1)
random_from_wiki_2000_rp26_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp26_dim$X3)
random_from_wiki_2000_rp28_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp28_dim$X1)
random_from_wiki_2000_rp28_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp28_dim$X3)
random_from_wiki_2000_rp30_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp30_dim$X1)
random_from_wiki_2000_rp30_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp30_dim$X3)

random_from_wiki_2000_rp2_dim<- matrix(as.numeric(random_from_wiki_2000_rp2_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp4_dim<- matrix(as.numeric(random_from_wiki_2000_rp4_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp6_dim<- matrix(as.numeric(random_from_wiki_2000_rp6_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp8_dim<- matrix(as.numeric(random_from_wiki_2000_rp8_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp10_dim<- matrix(as.numeric(random_from_wiki_2000_rp10_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp12_dim<- matrix(as.numeric(random_from_wiki_2000_rp12_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp14_dim<- matrix(as.numeric(random_from_wiki_2000_rp14_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp16_dim<- matrix(as.numeric(random_from_wiki_2000_rp16_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp18_dim<- matrix(as.numeric(random_from_wiki_2000_rp18_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp20_dim<- matrix(as.numeric(random_from_wiki_2000_rp20_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp22_dim<- matrix(as.numeric(random_from_wiki_2000_rp22_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp24_dim<- matrix(as.numeric(random_from_wiki_2000_rp24_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp26_dim<- matrix(as.numeric(random_from_wiki_2000_rp26_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp28_dim<- matrix(as.numeric(random_from_wiki_2000_rp28_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp30_dim<- matrix(as.numeric(random_from_wiki_2000_rp30_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(random_from_wiki_2000_rp2_dim, random_from_wiki_2000_rp4_dim, random_from_wiki_2000_rp6_dim, random_from_wiki_2000_rp8_dim, random_from_wiki_2000_rp10_dim, random_from_wiki_2000_rp12_dim, random_from_wiki_2000_rp14_dim, random_from_wiki_2000_rp16_dim, random_from_wiki_2000_rp18_dim, random_from_wiki_2000_rp20_dim, random_from_wiki_2000_rp22_dim, random_from_wiki_2000_rp24_dim, random_from_wiki_2000_rp26_dim, random_from_wiki_2000_rp28_dim, random_from_wiki_2000_rp30_dim, wiki_sample1_dim, wiki_sample2_dim, wiki_sample3_dim, wiki_sample4_dim, wiki_sample5_dim, wiki_sample6_dim, wiki_sample7_dim, wiki_sample8_dim, wiki_sample9_dim, wiki_sample10_dim, wiki_sample11_dim, wiki_sample12_dim, wiki_sample13_dim, wiki_sample14_dim, wiki_sample15_dim), dim=c(20,20,30))

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,1:15])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,16:30])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,1]-x1[1,j])^2,(large_scale[i,j,2]-x1[1,j])^2,(large_scale[i,j,3]-x1[1,j])^2,(large_scale[i,j,4]-x1[1,j])^2,(large_scale[i,j,5]-x1[1,j])^2,(large_scale[i,j,6]-x1[1,j])^2,(large_scale[i,j,7]-x1[1,j])^2,(large_scale[i,j,8]-x1[1,j])^2,(large_scale[i,j,9]-x1[1,j])^2,(large_scale[i,j,10]-x1[1,j])^2,(large_scale[i,j,11]-x1[1,j])^2,(large_scale[i,j,12]-x1[1,j])^2,(large_scale[i,j,13]-x1[1,j])^2,(large_scale[i,j,14]-x1[1,j])^2, (large_scale[i,j,15]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,16]-x2[1,j])^2,(large_scale[i,j,17]-x2[1,j])^2,(large_scale[i,j,18]-x2[1,j])^2,
                 (large_scale[i,j,19]-x2[1,j])^2,(large_scale[i,j,20]-x2[1,j])^2,(large_scale[i,j,21]-x2[1,j])^2,(large_scale[i,j,22]-x2[1,j])^2,(large_scale[i,j,23]-x2[1,j])^2,(large_scale[i,j,24]-x2[1,j])^2,(large_scale[i,j,25]-x2[1,j])^2,(large_scale[i,j,26]-x2[1,j])^2,(large_scale[i,j,27]-x2[1,j])^2,(large_scale[i,j,28]-x2[1,j])^2,(large_scale[i,j,29]-x2[1,j])^2,(large_scale[i,j,30]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/28*1/30
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
hist(t)
z<- qnorm(pt(t,28))
z[is.na(z)]<- 0
hist(z)

null_dist<- density(z_null)
hist(z,30)
lines(null_dist)

h<-hist(z_null, breaks=5) 
xfit<-seq(min(z_null),max(z_null),length=40) 
yfit<-dnorm(xfit,mean=mean(z_null),sd=sd(z_null)) 
yfit <- yfit*diff(h$mids[1:2])*length(z_null)  
lines(xfit, yfit, col="blue", lwd=2)

hist(z,30,ylim=c(0,350),xlab="z-scores", main="Histogram of z-scores")
lines(xfit, yfit, col="blue", lwd=2)

sum(z>quantile(z_null,1-0.025/400),na.rm = T)+sum(z<quantile(z_null,0.025/400),na.rm = T)
table<- z
table_01<- ifelse((z>quantile(z_null,1-0.025/400)|z<quantile(z_null,0.025/400)),1,0)

### at most, we have 30 random vectors, maybe that is not a small change, need to do smaller changes
```
 
### replace just 2 and 30, and compare

### replacement datasets for random_from_wiki (smaller changes)
```{r}
options(scipen=999)
random_from_wiki_2000 <- read_delim("~/random_from_wiki_2000.txt"," ", escape_double = FALSE, trim_ws = TRUE)
random1_2000 <- read_delim("~/random1_2000.txt", " ", escape_double = FALSE, trim_ws = TRUE)
random_from_wiki_2000<- random_from_wiki_2000[4:2003,]
random1_2000<- random1_2000[4:2003,]
random_from_wiki_2000<- matrix(as.numeric(unlist(random_from_wiki_2000)),nrow=2000)
random1_2000<- matrix(as.numeric(unlist(random1_2000)),nrow=2000)

### rp 1
rp<- sample(1:2000,1)
random_from_wiki_2000_rp1<- random_from_wiki_2000
random_from_wiki_2000_rp1[rp,1:200]<- random1_2000[rp,1:200]

### rp 3
rp<- sample(1:2000,3)
random_from_wiki_2000_rp3<- random_from_wiki_2000
random_from_wiki_2000_rp3[rp,1:200]<- random1_2000[rp,1:200]

### rp 5
rp<- sample(1:2000,5)
random_from_wiki_2000_rp5<- random_from_wiki_2000
random_from_wiki_2000_rp5[rp,1:200]<- random1_2000[rp,1:200]


### rp 7
rp<- sample(1:2000,7)
random_from_wiki_2000_rp7<- random_from_wiki_2000
random_from_wiki_2000_rp7[rp,1:200]<- random1_2000[rp,1:200]


### rp 9
rp<- sample(1:2000,9)
random_from_wiki_2000_rp9<- random_from_wiki_2000
random_from_wiki_2000_rp9[rp,1:200]<- random1_2000[rp,1:200]


### rp 11
rp<- sample(1:2000,11)
random_from_wiki_2000_rp11<- random_from_wiki_2000
random_from_wiki_2000_rp11[rp,1:200]<- random1_2000[rp,1:200]


### rp 13
rp<- sample(1:2000,13)
random_from_wiki_2000_rp13<- random_from_wiki_2000
random_from_wiki_2000_rp13[rp,1:200]<- random1_2000[rp,1:200]


### rp 15
rp<- sample(1:2000,15)
random_from_wiki_2000_rp15<- random_from_wiki_2000
random_from_wiki_2000_rp15[rp,1:200]<- random1_2000[rp,1:200]

# write.table(random_from_wiki_2000_rp1, "random_from_wiki_2000_rp1.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp3, "random_from_wiki_2000_rp3.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp5, "random_from_wiki_2000_rp5.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp7, "random_from_wiki_2000_rp7.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp9, "random_from_wiki_2000_rp9.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp11, "random_from_wiki_2000_rp11.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp13, "random_from_wiki_2000_rp13.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_from_wiki_2000_rp15, "random_from_wiki_2000_rp15.txt",row.names=FALSE, na="", col.names = FALSE)

```

### large scale testing on replacement datasets (random_from_wiki)
```{r}
random_from_wiki_2000_rp1_dim<- read_csv("~/random_from_wiki_2000_rp1_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp2_dim<- read_csv("~/random_from_wiki_2000_rp2_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp3_dim<- read_csv("~/random_from_wiki_2000_rp3_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp4_dim<- read_csv("~/random_from_wiki_2000_rp4_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp5_dim<- read_csv("~/random_from_wiki_2000_rp5_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp6_dim<- read_csv("~/random_from_wiki_2000_rp6_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp7_dim<- read_csv("~/random_from_wiki_2000_rp7_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp8_dim<- read_csv("~/random_from_wiki_2000_rp8_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp9_dim<- read_csv("~/random_from_wiki_2000_rp9_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp10_dim<- read_csv("~/random_from_wiki_2000_rp10_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp11_dim<- read_csv("~/random_from_wiki_2000_rp11_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp12_dim<- read_csv("~/random_from_wiki_2000_rp12_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp13_dim<- read_csv("~/random_from_wiki_2000_rp13_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp14_dim<- read_csv("~/random_from_wiki_2000_rp14_H0_dim.txt", col_names = FALSE)
random_from_wiki_2000_rp15_dim<- read_csv("~/random_from_wiki_2000_rp15_H0_dim.txt", col_names = FALSE)

random_from_wiki_2000_rp1_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp1_dim$X1)
random_from_wiki_2000_rp1_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp1_dim$X3)
random_from_wiki_2000_rp2_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp2_dim$X1)
random_from_wiki_2000_rp2_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp2_dim$X3)
random_from_wiki_2000_rp3_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp3_dim$X1)
random_from_wiki_2000_rp3_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp3_dim$X3)
random_from_wiki_2000_rp4_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp4_dim$X1)
random_from_wiki_2000_rp4_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp4_dim$X3)
random_from_wiki_2000_rp5_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp5_dim$X1)
random_from_wiki_2000_rp5_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp5_dim$X3)
random_from_wiki_2000_rp6_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp6_dim$X1)
random_from_wiki_2000_rp6_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp6_dim$X3)
random_from_wiki_2000_rp7_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp7_dim$X1)
random_from_wiki_2000_rp7_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp7_dim$X3)
random_from_wiki_2000_rp8_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp8_dim$X1)
random_from_wiki_2000_rp8_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp8_dim$X3)
random_from_wiki_2000_rp9_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp9_dim$X1)
random_from_wiki_2000_rp9_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp9_dim$X3)
random_from_wiki_2000_rp10_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp10_dim$X1)
random_from_wiki_2000_rp10_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp10_dim$X3)
random_from_wiki_2000_rp11_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp11_dim$X1)
random_from_wiki_2000_rp11_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp11_dim$X3)
random_from_wiki_2000_rp12_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp12_dim$X1)
random_from_wiki_2000_rp12_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp12_dim$X3)
random_from_wiki_2000_rp13_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp13_dim$X1)
random_from_wiki_2000_rp13_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp13_dim$X3)
random_from_wiki_2000_rp14_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp14_dim$X1)
random_from_wiki_2000_rp14_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp14_dim$X3)
random_from_wiki_2000_rp15_dim$X1<- gsub("[^0-9]", "",random_from_wiki_2000_rp15_dim$X1)
random_from_wiki_2000_rp15_dim$X3<- gsub("[^0-9]", "",random_from_wiki_2000_rp15_dim$X3)

random_from_wiki_2000_rp1_dim<- matrix(as.numeric(random_from_wiki_2000_rp1_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp2_dim<- matrix(as.numeric(random_from_wiki_2000_rp2_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp3_dim<- matrix(as.numeric(random_from_wiki_2000_rp3_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp4_dim<- matrix(as.numeric(random_from_wiki_2000_rp4_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp5_dim<- matrix(as.numeric(random_from_wiki_2000_rp5_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp6_dim<- matrix(as.numeric(random_from_wiki_2000_rp6_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp7_dim<- matrix(as.numeric(random_from_wiki_2000_rp7_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp8_dim<- matrix(as.numeric(random_from_wiki_2000_rp8_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp9_dim<- matrix(as.numeric(random_from_wiki_2000_rp9_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp10_dim<- matrix(as.numeric(random_from_wiki_2000_rp10_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp11_dim<- matrix(as.numeric(random_from_wiki_2000_rp11_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp12_dim<- matrix(as.numeric(random_from_wiki_2000_rp12_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp13_dim<- matrix(as.numeric(random_from_wiki_2000_rp13_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp14_dim<- matrix(as.numeric(random_from_wiki_2000_rp14_dim$X3), ncol=20, byrow=F)
random_from_wiki_2000_rp15_dim<- matrix(as.numeric(random_from_wiki_2000_rp15_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(random_from_wiki_2000_rp1_dim, random_from_wiki_2000_rp2_dim, random_from_wiki_2000_rp3_dim, random_from_wiki_2000_rp4_dim, random_from_wiki_2000_rp5_dim, random_from_wiki_2000_rp6_dim, random_from_wiki_2000_rp7_dim, random_from_wiki_2000_rp8_dim, random_from_wiki_2000_rp9_dim, random_from_wiki_2000_rp10_dim, random_from_wiki_2000_rp11_dim, random_from_wiki_2000_rp12_dim, random_from_wiki_2000_rp13_dim, random_from_wiki_2000_rp14_dim, random_from_wiki_2000_rp15_dim, wiki_sample1_dim, wiki_sample2_dim, wiki_sample3_dim, wiki_sample4_dim, wiki_sample5_dim, wiki_sample6_dim, wiki_sample7_dim, wiki_sample8_dim, wiki_sample9_dim, wiki_sample10_dim, wiki_sample11_dim, wiki_sample12_dim, wiki_sample13_dim, wiki_sample14_dim, wiki_sample15_dim), dim=c(20,20,30))

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,1:15])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,16:30])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,1]-x1[1,j])^2,(large_scale[i,j,2]-x1[1,j])^2,(large_scale[i,j,3]-x1[1,j])^2,(large_scale[i,j,4]-x1[1,j])^2,(large_scale[i,j,5]-x1[1,j])^2,(large_scale[i,j,6]-x1[1,j])^2,(large_scale[i,j,7]-x1[1,j])^2,(large_scale[i,j,8]-x1[1,j])^2,(large_scale[i,j,9]-x1[1,j])^2,(large_scale[i,j,10]-x1[1,j])^2,(large_scale[i,j,11]-x1[1,j])^2,(large_scale[i,j,12]-x1[1,j])^2,(large_scale[i,j,13]-x1[1,j])^2,(large_scale[i,j,14]-x1[1,j])^2, (large_scale[i,j,15]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,16]-x2[1,j])^2,(large_scale[i,j,17]-x2[1,j])^2,(large_scale[i,j,18]-x2[1,j])^2,
                 (large_scale[i,j,19]-x2[1,j])^2,(large_scale[i,j,20]-x2[1,j])^2,(large_scale[i,j,21]-x2[1,j])^2,(large_scale[i,j,22]-x2[1,j])^2,(large_scale[i,j,23]-x2[1,j])^2,(large_scale[i,j,24]-x2[1,j])^2,(large_scale[i,j,25]-x2[1,j])^2,(large_scale[i,j,26]-x2[1,j])^2,(large_scale[i,j,27]-x2[1,j])^2,(large_scale[i,j,28]-x2[1,j])^2,(large_scale[i,j,29]-x2[1,j])^2,(large_scale[i,j,30]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/28*1/30
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
hist(t)
z<- qnorm(pt(t,28))
z[is.na(z)]<- 0
hist(z)

null_dist<- density(z_null)
hist(z,30)
lines(null_dist)

h<-hist(z_null, breaks=5) 
xfit<-seq(min(z_null),max(z_null),length=40) 
yfit<-dnorm(xfit,mean=mean(z_null),sd=sd(z_null)) 
yfit <- yfit*diff(h$mids[1:2])*length(z_null)  
lines(xfit, yfit, col="blue", lwd=2)

hist(z,30,ylim=c(0,350),xlab="z-scores", main="Histogram of z-scores")
lines(xfit, yfit, col="blue", lwd=2)

sum(z>quantile(z_null,1-0.025/400),na.rm = T)+sum(z<quantile(z_null,0.025/400),na.rm = T)
table<- z
table_01_random_from_wiki<- ifelse((z>quantile(z_null,1-0.025/400)|z<quantile(z_null,0.025/400)),1,0)

```


### large scale testing on rp (random data, and introduce wiki vectors)
### null distribution

```{r}
random1_dim<- read_csv("~/random1_dim.txt", col_names = FALSE)
random2_dim<- read_csv("~/random2_dim.txt", col_names = FALSE)
random3_dim<- read_csv("~/random3_dim.txt", col_names = FALSE)
random4_dim<- read_csv("~/random4_dim.txt", col_names = FALSE)
random5_dim<- read_csv("~/random5_dim.txt", col_names = FALSE)
random6_dim<- read_csv("~/random6_dim.txt", col_names = FALSE)
random7_dim<- read_csv("~/random7_dim.txt", col_names = FALSE)
random8_dim<- read_csv("~/random8_dim.txt", col_names = FALSE)
random9_dim<- read_csv("~/random9_dim.txt", col_names = FALSE)
random10_dim<- read_csv("~/random10_dim.txt", col_names = FALSE)
random11_dim<- read_csv("~/random11_dim.txt", col_names = FALSE)
random12_dim<- read_csv("~/random12_dim.txt", col_names = FALSE)
random13_dim<- read_csv("~/random13_dim.txt", col_names = FALSE)
random14_dim<- read_csv("~/random14_dim.txt", col_names = FALSE)
random15_dim<- read_csv("~/random15_dim.txt", col_names = FALSE)

random1_dim$X1<- gsub("[^0-9]", "",random1_dim$X1)
random1_dim$X3<- gsub("[^0-9]", "",random1_dim$X3)
random2_dim$X1<- gsub("[^0-9]", "",random2_dim$X1)
random2_dim$X3<- gsub("[^0-9]", "",random2_dim$X3)
random3_dim$X1<- gsub("[^0-9]", "",random3_dim$X1)
random3_dim$X3<- gsub("[^0-9]", "",random3_dim$X3)
random4_dim$X1<- gsub("[^0-9]", "",random4_dim$X1)
random4_dim$X3<- gsub("[^0-9]", "",random4_dim$X3)
random5_dim$X1<- gsub("[^0-9]", "",random5_dim$X1)
random5_dim$X3<- gsub("[^0-9]", "",random5_dim$X3)
random6_dim$X1<- gsub("[^0-9]", "",random6_dim$X1)
random6_dim$X3<- gsub("[^0-9]", "",random6_dim$X3)
random7_dim$X1<- gsub("[^0-9]", "",random7_dim$X1)
random7_dim$X3<- gsub("[^0-9]", "",random7_dim$X3)
random8_dim$X1<- gsub("[^0-9]", "",random8_dim$X1)
random8_dim$X3<- gsub("[^0-9]", "",random8_dim$X3)
random9_dim$X1<- gsub("[^0-9]", "",random9_dim$X1)
random9_dim$X3<- gsub("[^0-9]", "",random9_dim$X3)
random10_dim$X1<- gsub("[^0-9]", "",random10_dim$X1)
random10_dim$X3<- gsub("[^0-9]", "",random10_dim$X3)
random11_dim$X1<- gsub("[^0-9]", "",random11_dim$X1)
random11_dim$X3<- gsub("[^0-9]", "",random11_dim$X3)
random12_dim$X1<- gsub("[^0-9]", "",random12_dim$X1)
random12_dim$X3<- gsub("[^0-9]", "",random12_dim$X3)
random13_dim$X1<- gsub("[^0-9]", "",random13_dim$X1)
random13_dim$X3<- gsub("[^0-9]", "",random13_dim$X3)
random14_dim$X1<- gsub("[^0-9]", "",random14_dim$X1)
random14_dim$X3<- gsub("[^0-9]", "",random14_dim$X3)
random15_dim$X1<- gsub("[^0-9]", "",random15_dim$X1)
random15_dim$X3<- gsub("[^0-9]", "",random15_dim$X3)

random1_dim<- matrix(as.numeric(random1_dim$X3), ncol=20, byrow=F)
random2_dim<- matrix(as.numeric(random2_dim$X3), ncol=20, byrow=F)
random3_dim<- matrix(as.numeric(random3_dim$X3), ncol=20, byrow=F)
random4_dim<- matrix(as.numeric(random4_dim$X3), ncol=20, byrow=F)
random5_dim<- matrix(as.numeric(random5_dim$X3), ncol=20, byrow=F)
random6_dim<- matrix(as.numeric(random6_dim$X3), ncol=20, byrow=F)
random7_dim<- matrix(as.numeric(random7_dim$X3), ncol=20, byrow=F)
random8_dim<- matrix(as.numeric(random8_dim$X3), ncol=20, byrow=F)
random9_dim<- matrix(as.numeric(random9_dim$X3), ncol=20, byrow=F)
random10_dim<- matrix(as.numeric(random10_dim$X3), ncol=20, byrow=F)
random11_dim<- matrix(as.numeric(random11_dim$X3), ncol=20, byrow=F)
random12_dim<- matrix(as.numeric(random12_dim$X3), ncol=20, byrow=F)
random13_dim<- matrix(as.numeric(random13_dim$X3), ncol=20, byrow=F)
random14_dim<- matrix(as.numeric(random14_dim$X3), ncol=20, byrow=F)
random15_dim<- matrix(as.numeric(random15_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(random1_dim, random2_dim, random3_dim, random4_dim, random5_dim, random6_dim, random7_dim, random8_dim, random9_dim, random10_dim, random11_dim, random12_dim, random13_dim, random14_dim, random15_dim), dim=c(20,20,15))


allt<- array(0,dim=c(20,20,500))
for (m in 1:500){

group1<- sample(1:15,7)  
all<- seq(1,15,1)
group2<- all[is.na(pmatch(all,group1))]

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,group1])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,group2])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,group1[1]]-x1[1,j])^2,(large_scale[i,j,group1[2]]-x1[1,j])^2,(large_scale[i,j,group1[3]]-x1[1,j])^2,(large_scale[i,j,group1[4]]-x1[1,j])^2,(large_scale[i,j,group1[5]]-x1[1,j])^2,(large_scale[i,j,group1[6]]-x1[1,j])^2,(large_scale[i,j,group1[7]]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,group2[1]]-x2[1,j])^2,(large_scale[i,j,group2[2]]-x2[1,j])^2,(large_scale[i,j,group2[3]]-x2[1,j])^2,
                 (large_scale[i,j,group2[4]]-x2[1,j])^2,(large_scale[i,j,group2[5]]-x2[1,j])^2,(large_scale[i,j,group2[6]]-x2[1,j])^2,(large_scale[i,j,group2[7]]-x2[1,j])^2,(large_scale[i,j,group2[8]]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/13*1/15
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
allt[,,m] <- t
print(m)
}

allt[is.na(allt)]<- 0
cvt<- matrix(0,ncol=20,nrow=20)

for (i in 1:20){
  for (j in 1:20){
    cvt[i,j]<- mean(allt[i,j,1:20])
  }
}

#hist(allt)
z<- qnorm(pt(cvt,13))
z_null<- z
z_null[is.na(z_null)] <- 0
hist(z_null,30)

qqnorm(z_null)
qqline(z_null)
```

### replacement data sets created (random 1 as the original)
```{r}
options(scipen=999)
random_from_wiki_2000 <- read_delim("~/random_from_wiki_2000.txt"," ", escape_double = FALSE, trim_ws = TRUE)
random1_2000 <- read_delim("~/random1_2000.txt", " ", escape_double = FALSE, trim_ws = TRUE)
random_from_wiki_2000<- random_from_wiki_2000[4:2003,]
random1_2000<- random1_2000[4:2003,]
random_from_wiki_2000<- matrix(as.numeric(unlist(random_from_wiki_2000)),nrow=2000)
random1_2000<- matrix(as.numeric(unlist(random1_2000)),nrow=2000)

### rp 1
rp<- sample(1:2000,1)
random_rp1<- random1_2000
random_rp1[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 2
rp<- sample(1:2000,2)
random_rp2<- random1_2000
random_rp2[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 3
rp<- sample(1:2000,3)
random_rp3<- random1_2000
random_rp3[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 4
rp<- sample(1:2000,4)
random_rp4<- random1_2000
random_rp4[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 5
rp<- sample(1:2000,5)
random_rp5<- random1_2000
random_rp5[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 6
rp<- sample(1:2000,6)
random_rp6<- random1_2000
random_rp6[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 7
rp<- sample(1:2000,7)
random_rp7<- random1_2000
random_rp7[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 8
rp<- sample(1:2000,8)
random_rp8<- random1_2000
random_rp8[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 9
rp<- sample(1:2000,9)
random_rp9<- random1_2000
random_rp9[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 10
rp<- sample(1:2000,10)
random_rp10<- random1_2000
random_rp10[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 11
rp<- sample(1:2000,11)
random_rp11<- random1_2000
random_rp11[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 12
rp<- sample(1:2000,12)
random_rp12<- random1_2000
random_rp12[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 13
rp<- sample(1:2000,13)
random_rp13<- random1_2000
random_rp13[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 14
rp<- sample(1:2000,14)
random_rp14<- random1_2000
random_rp14[rp,1:200]<- random_from_wiki_2000[rp,1:200]

### rp 15
rp<- sample(1:2000,15)
random_rp15<- random1_2000
random_rp15[rp,1:200]<- random_from_wiki_2000[rp,1:200]
# 
# write.table(random_rp1, "random_rp1.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp2, "random_rp2.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp3, "random_rp3.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp4, "random_rp4.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp5, "random_rp5.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp6, "random_rp6.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp7, "random_rp7.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp8, "random_rp8.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp9, "random_rp9.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp10, "random_rp10.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp11, "random_rp11.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp12, "random_rp12.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp13, "random_rp13.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp14, "random_rp14.txt",row.names=FALSE, na="", col.names = FALSE)
# write.table(random_rp15, "random_rp15.txt",row.names=FALSE, na="", col.names = FALSE)

```

### Alternatives (random with rp)
```{r}
random_rp1_dim<- read_csv("~/random_rp1_H0_dim.txt", col_names = FALSE)
random_rp2_dim<- read_csv("~/random_rp2_H0_dim.txt", col_names = FALSE)
random_rp3_dim<- read_csv("~/random_rp3_H0_dim.txt", col_names = FALSE)
random_rp4_dim<- read_csv("~/random_rp4_H0_dim.txt", col_names = FALSE)
random_rp5_dim<- read_csv("~/random_rp5_H0_dim.txt", col_names = FALSE)
random_rp6_dim<- read_csv("~/random_rp6_H0_dim.txt", col_names = FALSE)
random_rp7_dim<- read_csv("~/random_rp7_H0_dim.txt", col_names = FALSE)
random_rp8_dim<- read_csv("~/random_rp8_H0_dim.txt", col_names = FALSE)
random_rp9_dim<- read_csv("~/random_rp9_H0_dim.txt", col_names = FALSE)
random_rp10_dim<- read_csv("~/random_rp10_H0_dim.txt", col_names = FALSE)
random_rp11_dim<- read_csv("~/random_rp11_H0_dim.txt", col_names = FALSE)
random_rp12_dim<- read_csv("~/random_rp12_H0_dim.txt", col_names = FALSE)
random_rp13_dim<- read_csv("~/random_rp13_H0_dim.txt", col_names = FALSE)
random_rp14_dim<- read_csv("~/random_rp14_H0_dim.txt", col_names = FALSE)
random_rp15_dim<- read_csv("~/random_rp15_H0_dim.txt", col_names = FALSE)

random_rp1_dim$X1<- gsub("[^0-9]", "",random_rp1_dim$X1)
random_rp1_dim$X3<- gsub("[^0-9]", "",random_rp1_dim$X3)
random_rp2_dim$X1<- gsub("[^0-9]", "",random_rp2_dim$X1)
random_rp2_dim$X3<- gsub("[^0-9]", "",random_rp2_dim$X3)
random_rp3_dim$X1<- gsub("[^0-9]", "",random_rp3_dim$X1)
random_rp3_dim$X3<- gsub("[^0-9]", "",random_rp3_dim$X3)
random_rp4_dim$X1<- gsub("[^0-9]", "",random_rp4_dim$X1)
random_rp4_dim$X3<- gsub("[^0-9]", "",random_rp4_dim$X3)
random_rp5_dim$X1<- gsub("[^0-9]", "",random_rp5_dim$X1)
random_rp5_dim$X3<- gsub("[^0-9]", "",random_rp5_dim$X3)
random_rp6_dim$X1<- gsub("[^0-9]", "",random_rp6_dim$X1)
random_rp6_dim$X3<- gsub("[^0-9]", "",random_rp6_dim$X3)
random_rp7_dim$X1<- gsub("[^0-9]", "",random_rp7_dim$X1)
random_rp7_dim$X3<- gsub("[^0-9]", "",random_rp7_dim$X3)
random_rp8_dim$X1<- gsub("[^0-9]", "",random_rp8_dim$X1)
random_rp8_dim$X3<- gsub("[^0-9]", "",random_rp8_dim$X3)
random_rp9_dim$X1<- gsub("[^0-9]", "",random_rp9_dim$X1)
random_rp9_dim$X3<- gsub("[^0-9]", "",random_rp9_dim$X3)
random_rp10_dim$X1<- gsub("[^0-9]", "",random_rp10_dim$X1)
random_rp10_dim$X3<- gsub("[^0-9]", "",random_rp10_dim$X3)
random_rp11_dim$X1<- gsub("[^0-9]", "",random_rp11_dim$X1)
random_rp11_dim$X3<- gsub("[^0-9]", "",random_rp11_dim$X3)
random_rp12_dim$X1<- gsub("[^0-9]", "",random_rp12_dim$X1)
random_rp12_dim$X3<- gsub("[^0-9]", "",random_rp12_dim$X3)
random_rp13_dim$X1<- gsub("[^0-9]", "",random_rp13_dim$X1)
random_rp13_dim$X3<- gsub("[^0-9]", "",random_rp13_dim$X3)
random_rp14_dim$X1<- gsub("[^0-9]", "",random_rp14_dim$X1)
random_rp14_dim$X3<- gsub("[^0-9]", "",random_rp14_dim$X3)
random_rp15_dim$X1<- gsub("[^0-9]", "",random_rp15_dim$X1)
random_rp15_dim$X3<- gsub("[^0-9]", "",random_rp15_dim$X3)

random_rp1_dim<- matrix(as.numeric(random_rp1_dim$X3), ncol=20, byrow=F)
random_rp2_dim<- matrix(as.numeric(random_rp2_dim$X3), ncol=20, byrow=F)
random_rp3_dim<- matrix(as.numeric(random_rp3_dim$X3), ncol=20, byrow=F)
random_rp4_dim<- matrix(as.numeric(random_rp4_dim$X3), ncol=20, byrow=F)
random_rp5_dim<- matrix(as.numeric(random_rp5_dim$X3), ncol=20, byrow=F)
random_rp6_dim<- matrix(as.numeric(random_rp6_dim$X3), ncol=20, byrow=F)
random_rp7_dim<- matrix(as.numeric(random_rp7_dim$X3), ncol=20, byrow=F)
random_rp8_dim<- matrix(as.numeric(random_rp8_dim$X3), ncol=20, byrow=F)
random_rp9_dim<- matrix(as.numeric(random_rp9_dim$X3), ncol=20, byrow=F)
random_rp10_dim<- matrix(as.numeric(random_rp10_dim$X3), ncol=20, byrow=F)
random_rp11_dim<- matrix(as.numeric(random_rp11_dim$X3), ncol=20, byrow=F)
random_rp12_dim<- matrix(as.numeric(random_rp12_dim$X3), ncol=20, byrow=F)
random_rp13_dim<- matrix(as.numeric(random_rp13_dim$X3), ncol=20, byrow=F)
random_rp14_dim<- matrix(as.numeric(random_rp14_dim$X3), ncol=20, byrow=F)
random_rp15_dim<- matrix(as.numeric(random_rp15_dim$X3), ncol=20, byrow=F)

large_scale<- array(c(random_rp1_dim, random_rp2_dim, random_rp3_dim, random_rp4_dim, random_rp5_dim, random_rp6_dim, random_rp7_dim, random_rp8_dim, random_rp9_dim, random_rp10_dim, random_rp11_dim, random_rp12_dim, random_rp13_dim, random_rp14_dim, random_rp15_dim, random1_dim, random2_dim, random3_dim, random4_dim, random5_dim, random6_dim, random7_dim, random8_dim, random9_dim, random10_dim, random11_dim, random12_dim, random13_dim, random14_dim, random15_dim), dim=c(20,20,30))

x1<- c()
x2<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_mean<- mean(large_scale[i,j,1:15])
    x1<- c(x1,x1_mean)
    x2_mean<- mean(large_scale[i,j,16:30])
    x2<- c(x2,x2_mean)
  }
}

x1<- matrix(x1,ncol=20, byrow=T)
x2<- matrix(x2,ncol=20, byrow=T)

x1_s<- c()
x2_s<- c()

for (i in 1:20){
  for (j in 1:20){
    x1_sqr<- sum((large_scale[i,j,1]-x1[1,j])^2,(large_scale[i,j,2]-x1[1,j])^2,(large_scale[i,j,3]-x1[1,j])^2,(large_scale[i,j,4]-x1[1,j])^2,(large_scale[i,j,5]-x1[1,j])^2,(large_scale[i,j,6]-x1[1,j])^2,(large_scale[i,j,7]-x1[1,j])^2,(large_scale[i,j,8]-x1[1,j])^2,(large_scale[i,j,9]-x1[1,j])^2,(large_scale[i,j,10]-x1[1,j])^2,(large_scale[i,j,11]-x1[1,j])^2,(large_scale[i,j,12]-x1[1,j])^2,(large_scale[i,j,13]-x1[1,j])^2,(large_scale[i,j,14]-x1[1,j])^2, (large_scale[i,j,15]-x1[1,j])^2)
    x1_s<- c(x1_s,x1_sqr)
    x2_sqr<- sum((large_scale[i,j,16]-x2[1,j])^2,(large_scale[i,j,17]-x2[1,j])^2,(large_scale[i,j,18]-x2[1,j])^2,
                 (large_scale[i,j,19]-x2[1,j])^2,(large_scale[i,j,20]-x2[1,j])^2,(large_scale[i,j,21]-x2[1,j])^2,(large_scale[i,j,22]-x2[1,j])^2,(large_scale[i,j,23]-x2[1,j])^2,(large_scale[i,j,24]-x2[1,j])^2,(large_scale[i,j,25]-x2[1,j])^2,(large_scale[i,j,26]-x2[1,j])^2,(large_scale[i,j,27]-x2[1,j])^2,(large_scale[i,j,28]-x2[1,j])^2,(large_scale[i,j,29]-x2[1,j])^2,(large_scale[i,j,30]-x2[1,j])^2)
    x2_s<- c(x2_s,x2_sqr)
  }
}

s_sqr<- (x1_s+x2_s)/28*1/30
s_sqr<- matrix(s_sqr,ncol=20, byrow=T)
t<- (x2-x1)/sqrt(s_sqr)
hist(t)
z<- qnorm(pt(t,28))
z[is.na(z)]<- 0
hist(z)

null_dist<- density(z_null)
hist(z,30)
lines(null_dist)

h<-hist(z_null, breaks=5) 
xfit<-seq(min(z_null),max(z_null),length=40) 
yfit<-dnorm(xfit,mean=mean(z_null),sd=sd(z_null)) 
yfit <- yfit*diff(h$mids[1:2])*length(z_null)  
lines(xfit, yfit, col="blue", lwd=2)

hist(z,30,ylim=c(0,350),xlab="z-scores", main="Histogram of z-scores")
lines(xfit, yfit, col="blue", lwd=2)

sum(z>quantile(z_null,1-0.025/400),na.rm = T)+sum(z<quantile(z_null,0.025/400),na.rm = T)
table<- z
table_01_random<- ifelse((z>quantile(z_null,1-0.025/400)|z<quantile(z_null,0.025/400)),1,0)

```